---
title: "Processing LLMC outputs"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

# Goal

The goal of this notebook is to read in the 55 csv files of results and the six csv files of true answers and then process them for subsequent analysis.  (LifeEval has been archived — see `../archive/lifeeval/` — so its files are no longer read here.)  We will end up with one giant data frame (which we write to csv) that will have the following columns:

`llm`, `qset`, `question_id`, `stated_confidence`, `chosen_token_confidence`, `max_token_confidence`, `correct`.

We define these columns in terms of the following notation:

- $C_i^\text{stated}(k)$ is the stated confidence for choice $k$ in question $i$
- $C_i^\text{token}(k)$ is the token confidence for choice $k$ in question $i$
- $y_i$ is the correct answer
- $\hat y_i$ is an LLM's chosen answer

The column `stated_confidence` is $C_i^\text{stated}(\hat y_i)$, i.e. the stated confidence associated with the LLM's chosen answer.

The column `chosen_token_confidence` is $C_i^\text{token}(\hat y_i)$, i.e. the token-based confidence associated with the LLM's chosen answer.

The column `max_token_confidence` is $\max_kC_i^\text{token}(k)$, i.e. the token-based confidence associated with what the LLM would choose if temperature were 0.

# Load the data

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
```

```{r}
path <- "../"
csvs <- fs::dir_ls(file.path(path, "Parsed Results"),recurse = TRUE, glob="*csv")
```

There are 55 files of LLM results in total.  Let's extract the LLM and Qset for each file:

```{r}
stems <- csvs %>% fs::path_file() %>% str_remove(".csv")
llm <- stems %>% str_extract("[^_]+$")
qset <- stems %>% str_remove(paste0("_", llm))
```

```{r, message=FALSE}
all <- tibble(llm = llm, qset = qset, csv = csvs)
all <- all %>% mutate(dat = map(csv, read_csv, show_col_types=FALSE))
```
The problem alluded to above is when reading `Meta-Llama-3.1-70B-Instruct/boolq_valid_Meta-Llama-3.1-70B-Instruct.csv`. In row 1250 and column 2, it expected an empty string `""` but instead got an embedded null.  This does not sound concerning to me.

Let's also get the truth 

```{r}
truth_csvs <- fs::dir_ls(file.path(path, "Formatted Benchmarks"))
qset_truth_name <- fs::path_file(truth_csvs) %>% str_remove(".csv") %>% str_remove("_formatted")
truth <- map(truth_csvs, read_csv, show_col_types = FALSE)
names(truth) <- qset_truth_name
```

# Standardizing format

We will work our way through the 6 question sets, which have different formats.  Also, the GPT-4 and Llama models need to be treated differently because they also output token probabilities.

## Boolq

### GPT-4 and Llama models

Notice that after filtering based on coerce, we get all expected answers:

```{r}
all %>% 
  filter(qset == "boolq_valid", str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce) %>% 
  count(Answer, sort=TRUE)
```

```{r}
eval1 <- all %>% 
  filter(qset == "boolq_valid", str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce, Answer %in% c("True", "False")) %>% 
  select(llm, qset, `Question ID`, Answer, Confidence, True_prob, False_prob) %>% 
  transmute(
    llm,
    qset,
    question_id = `Question ID`,
    stated_confidence = Confidence,
    chosen_token_confidence = if_else(Answer == "True", True_prob, False_prob) / (True_prob + False_prob),
    max_token_confidence = pmax(True_prob, False_prob),
    answer = Answer == "True",
    stated_gini = 1 - Confidence^2 - (1 - Confidence)^2,
    token_gini = 1 - True_prob^2 - False_prob^2
    ) %>% 
  left_join(
    truth$boolq_valid %>% select(question_id = `Question ID`, `Correct Answer`),
    by = "question_id"
    ) %>% 
  mutate(
    correct = answer == `Correct Answer`
  ) %>% 
  select(-answer, -`Correct Answer`)
```


### Models without token probabilities

Before we can `unnest`, we need all the data frames to have the same format of columns.

```{r}
all %>% 
  filter(qset == "boolq_valid", !str_detect(llm, "Llama|gpt")) %>% 
  pull(dat) %>% 
  map_dfr(~ map_chr(.x, class))
```
We see that the `Answer` column for the first one (`claude-3-7-sonnet-20250219`) needs to be fixed.

```{r}
row <- which(all$qset == "boolq_valid" & all$llm == "claude-3-7-sonnet-20250219")
all[row,"dat"][[1]][[1]]$Answer <- ifelse(all[row,"dat"][[1]][[1]]$Answer, "True", "False")
```



```{r}
all %>% 
  filter(qset == "boolq_valid", !str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce) %>% 
  count(Answer, sort=TRUE)
```

```{r}
eval2 <- all %>% 
  filter(qset == "boolq_valid", !str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce) %>% 
  select(llm, qset, `Question ID`, Answer, Confidence) %>% 
  transmute(
    llm,
    qset,
    question_id = `Question ID`,
    stated_confidence = Confidence,
    answer = Answer == "True",
    stated_gini = 1 - Confidence^2 - (1 - Confidence)^2
    ) %>% 
  left_join(
    truth$boolq_valid %>% select(question_id = `Question ID`, `Correct Answer`),
    by = "question_id"
    ) %>% 
  mutate(
    correct = answer == `Correct Answer`
  ) %>% 
  select(-answer, -`Correct Answer`)
```



## LSAT

### GPT-4 and Llama models

Notice that we get all expected answers:

```{r}
all %>% 
  filter(qset == "lsat_ar_test", str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce) %>% 
  pull(Answer) %>% 
  unique() %>% 
  {. %in% c("A", "B", "C", "D", "E")} %>% 
  all() %>% 
  stopifnot()
```

Observe that the five probabilities don't always sum to 1 (but do so most of the time):

```{r}
all %>% 
  filter(qset == "lsat_ar_test", str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce) %>%
  mutate(prob_sum = A+B+C+D+E) %>% 
  ggplot(aes(x=prob_sum)) + geom_histogram()
```

```{r}
all %>% 
  filter(qset == "lsat_ar_test", str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce) %>%
  mutate(prob_sum = A_prob+B_prob+C_prob+D_prob+E_prob) %>% 
  ggplot(aes(x=prob_sum)) + geom_histogram()
```

The prereg says we will normalize the confidences, so let's do that:

```{r}
eval3 <- all %>% 
  filter(qset == "lsat_ar_test", str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce) %>%
  transmute(
    llm,
    qset,
    question_id = `Question ID`,
    Answer,
    prob_sum = A+B+C+D+E,
    stated_confidence = case_when(
      Answer == "A" ~ A,
      Answer == "B" ~ B,
      Answer == "C" ~ C,
      Answer == "D" ~ D,
      Answer == "E" ~ E,
    ) / if_else(prob_sum == 0, 1, prob_sum), # we take 0/0 to be 0.
    prob_token_sum = A_prob+B_prob+C_prob+D_prob+E_prob,
    chosen_token_confidence = case_when(
      Answer == "A" ~ A_prob,
      Answer == "B" ~ B_prob,
      Answer == "C" ~ C_prob,
      Answer == "D" ~ D_prob,
      Answer == "E" ~ E_prob,
    ) / if_else(prob_token_sum == 0, 1, prob_token_sum),
    max_token_confidence = pmax(A_prob, B_prob, C_prob, D_prob, E_prob) / if_else(prob_token_sum == 0, 1, prob_token_sum),
    stated_gini = 1 - (A^2 + B^2 + C^2 + D^2 + E^2) / if_else(prob_sum == 0, 1, prob_sum)^2,
    token_gini = 1 - (A_prob^2 + B_prob^2 + C_prob^2 + D_prob^2 + E_prob^2) / if_else(prob_token_sum == 0, 1, prob_token_sum)^2,
    ) %>% 
  left_join(
    truth$lsat_ar_test %>% select(question_id = `Question ID`, `Correct Answer Letter`),
    by = "question_id"
    ) %>% 
  mutate(
    correct = Answer == `Correct Answer Letter`
  ) %>% 
  select(-Answer, -`Correct Answer Letter`, -prob_sum, -prob_token_sum)
```

### Models without token probabilities


```{r}
all %>% 
  filter(qset == "lsat_ar_test", !str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce) %>% 
  count(Answer)
```

```{r}
all %>% 
  filter(qset == "lsat_ar_test", !str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce) %>%
  mutate(prob_sum = A+B+C+D+E) %>% 
  ggplot(aes(x=prob_sum)) + geom_histogram()
```

```{r}
eval4 <- all %>% 
  filter(qset == "lsat_ar_test", !str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce, Answer %in% LETTERS[1:5]) %>%
  transmute(
    llm,
    qset,
    question_id = `Question ID`,
    Answer,
    prob_sum = A+B+C+D+E,
    stated_confidence = case_when(
      Answer == "A" ~ A,
      Answer == "B" ~ B,
      Answer == "C" ~ C,
      Answer == "D" ~ D,
      Answer == "E" ~ E,
    ) / if_else(prob_sum == 0, 1, prob_sum), # we take 0/0 to be 0.
    stated_gini = 1 - (A^2 + B^2 + C^2 + D^2 + E^2) / if_else(prob_sum == 0, 1, prob_sum)^2
    ) %>% 
  left_join(
    truth$lsat_ar_test %>% select(question_id = `Question ID`, `Correct Answer Letter`),
    by = "question_id"
    ) %>% 
  mutate(
    correct = Answer == `Correct Answer Letter`
  ) %>% 
  select(-Answer, -`Correct Answer Letter`, -prob_sum)
```

## SAT

### GPT-4 and Llama models

```{r}
all %>% 
  filter(qset == "sat_en", str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce) %>% 
  count(Answer)
```
Let's look at the sums of the probabilities.

```{r}
all %>% 
  filter(qset == "sat_en", str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce) %>%
  mutate(prob_sum = A+B+C+D) %>% 
  ggplot(aes(x=prob_sum)) + geom_histogram()
```

There's a case where all probabilities are 0:

```{r}
all %>% 
  filter(qset == "sat_en", str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce) %>%
  mutate(prob_sum = A+B+C+D) %>% 
  filter(prob_sum == 0)
```

```{r}
all %>% 
  filter(qset == "sat_en", str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce) %>%
  mutate(prob_sum = A_prob+B_prob+C_prob+D_prob) %>% 
  ggplot(aes(x=prob_sum)) + geom_histogram()
```

```{r}
eval5 <- all %>% 
  filter(qset == "sat_en", str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce, Answer %in% LETTERS[1:4]) %>%
  transmute(
    llm,
    qset,
    question_id = `Question ID`,
    Answer,
    prob_sum = A+B+C+D,
    stated_confidence = case_when(
      Answer == "A" ~ A,
      Answer == "B" ~ B,
      Answer == "C" ~ C,
      Answer == "D" ~ D
    ) / if_else(prob_sum == 0, 1, prob_sum), # we take 0/0 to be 0.
    prob_token_sum = A_prob+B_prob+C_prob+D_prob,
    chosen_token_confidence = case_when(
      Answer == "A" ~ A_prob,
      Answer == "B" ~ B_prob,
      Answer == "C" ~ C_prob,
      Answer == "D" ~ D_prob
    ) / if_else(prob_token_sum == 0, 1, prob_token_sum),
    max_token_confidence = pmax(A_prob, B_prob, C_prob, D_prob) / if_else(prob_token_sum == 0, 1, prob_token_sum),
    stated_gini = 1 - (A^2 + B^2 + C^2 + D^2) / if_else(prob_sum == 0, 1, prob_sum)^2,
    token_gini = 1 - (A_prob^2 + B_prob^2 + C_prob^2 + D_prob^2) / if_else(prob_token_sum == 0, 1, prob_token_sum)^2
    ) %>% 
  left_join(
    truth$sat_en %>% select(question_id = `Question ID`, `Correct Answer Letter`),
    by = "question_id"
    ) %>% 
  mutate(
    correct = Answer == `Correct Answer Letter`
  ) %>% 
  select(-Answer, -`Correct Answer Letter`, -prob_sum, -prob_token_sum)
```

### Models without token probabilities


Notice that we get a non-compliant answer ("E").

```{r}
all %>% 
  filter(qset == "sat_en", !str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce) %>% 
  count(Answer)
```

Let's look at the sums of the probabilities.

```{r}
all %>% 
  filter(qset == "sat_en", !str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce) %>%
  mutate(prob_sum = A+B+C+D) %>% 
  ggplot(aes(x=prob_sum)) + geom_histogram()
```

```{r}
eval6 <- all %>% 
  filter(qset == "sat_en", !str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce, Answer %in% LETTERS[1:4]) %>%
  transmute(
    llm,
    qset,
    question_id = `Question ID`,
    Answer,
    prob_sum = A+B+C+D,
    stated_confidence = case_when(
      Answer == "A" ~ A,
      Answer == "B" ~ B,
      Answer == "C" ~ C,
      Answer == "D" ~ D
    ) / if_else(prob_sum == 0, 1, prob_sum), # we take 0/0 to be 0.
    stated_gini = 1 - (A^2 + B^2 + C^2 + D^2) / if_else(prob_sum == 0, 1, prob_sum)^2
    ) %>% 
  left_join(
    truth$sat_en %>% select(question_id = `Question ID`, `Correct Answer Letter`),
    by = "question_id"
    ) %>% 
  mutate(
    correct = Answer == `Correct Answer Letter`
  ) %>% 
  select(-Answer, -`Correct Answer Letter`, -prob_sum)
```

## Sciq

### GPT-4 and Llama models

All compliant answers:

```{r}
all %>% 
  filter(qset == "sciq_test", str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce) %>% 
  count(Answer)
```
Let's look at the sums of the probabilities.


```{r}
all %>% 
  filter(qset == "sciq_test", str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce) %>%
  mutate(prob_sum = A+B+C+D) %>% 
  ggplot(aes(x=prob_sum)) + geom_histogram()
```

```{r}
all %>% 
  filter(qset == "sciq_test", str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce) %>%
  mutate(prob_sum = A_prob+B_prob+C_prob+D_prob) %>% 
  ggplot(aes(x=prob_sum)) + geom_histogram()
```

```{r}
eval7 <- all %>% 
  filter(qset == "sciq_test", str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce, Answer %in% LETTERS[1:4]) %>%
  transmute(
    llm,
    qset,
    question_id = `Question ID`,
    Answer,
    prob_sum = A+B+C+D,
    stated_confidence = case_when(
      Answer == "A" ~ A,
      Answer == "B" ~ B,
      Answer == "C" ~ C,
      Answer == "D" ~ D
    ) / if_else(prob_sum == 0, 1, prob_sum), # we take 0/0 to be 0.
    prob_token_sum = A_prob+B_prob+C_prob+D_prob,
    chosen_token_confidence = case_when(
      Answer == "A" ~ A_prob,
      Answer == "B" ~ B_prob,
      Answer == "C" ~ C_prob,
      Answer == "D" ~ D_prob
    ) / if_else(prob_token_sum == 0, 1, prob_token_sum),
    max_token_confidence = pmax(A_prob, B_prob, C_prob, D_prob) / if_else(prob_token_sum == 0, 1, prob_token_sum),
    stated_gini = 1 - (A^2 + B^2 + C^2 + D^2) / if_else(prob_sum == 0, 1, prob_sum)^2,
    token_gini = 1 - (A_prob^2 + B_prob^2 + C_prob^2 + D_prob^2) / if_else(prob_token_sum == 0, 1, prob_token_sum)^2
    ) %>% 
  left_join(
    truth$sciq_test %>% select(question_id = `Question ID`, `Correct Answer Letter`),
    by = "question_id"
    ) %>% 
  mutate(
    correct = Answer == `Correct Answer Letter`
  ) %>% 
  select(-Answer, -`Correct Answer Letter`, -prob_sum, -prob_token_sum)
```

### Models without token probabilities

All compliant answers:

```{r}
all %>% 
  filter(qset == "sciq_test", !str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce) %>% 
  count(Answer)
```

Let's look at the sums of the probabilities.

```{r}
all %>% 
  filter(qset == "sciq_test", !str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce) %>%
  mutate(prob_sum = A+B+C+D) %>% 
  ggplot(aes(x=prob_sum)) + geom_histogram()
```

```{r}
eval8 <- all %>% 
  filter(qset == "sciq_test", !str_detect(llm, "Llama|gpt")) %>% 
  unnest(cols = dat) %>% 
  filter(coerce, Answer %in% LETTERS[1:4]) %>%
  transmute(
    llm,
    qset,
    question_id = `Question ID`,
    Answer,
    prob_sum = A+B+C+D,
    stated_confidence = case_when(
      Answer == "A" ~ A,
      Answer == "B" ~ B,
      Answer == "C" ~ C,
      Answer == "D" ~ D
    ) / if_else(prob_sum == 0, 1, prob_sum), # we take 0/0 to be 0.
    stated_gini = 1 - (A^2 + B^2 + C^2 + D^2) / if_else(prob_sum == 0, 1, prob_sum)^2
    ) %>% 
  left_join(
    truth$sciq_test %>% select(question_id = `Question ID`, `Correct Answer Letter`),
    by = "question_id"
    ) %>% 
  mutate(
    correct = Answer == `Correct Answer Letter`
  ) %>% 
  select(-Answer, -`Correct Answer Letter`, -prob_sum)
```

## halu_eval

For this Qset, we don't need to distinguish between models with/without token probabilities, because we do not get token probabilities.  Also, the format is pretty different, in that we don't have the models choose an answer, rather we seed it with a correct and a hallucinated answer, and ask for its (stated) confidence in each case.



```{r}
halu <- all %>% 
  filter(qset == "halu_eval_qa") %>% 
  unnest(cols = dat) %>% 
  filter(coerce)
```


```{r}
eval9 <- halu %>% 
  transmute(
    qset,
    llm,
    question_id = `Question ID`,
    stated_confidence = Confidence,
    correct = str_detect(question_id, "r")
    )
```

# Saving processed data

Let's start by combining the question set data frames:

```{r}
if (!dir.exists("processed")) dir.create("processed")
bind_rows(
  eval1,
  eval2,
  eval3,
  eval4,
  eval5,
  eval6,
  eval7,
  eval8
) %>% 
  mutate(question_id = as.character(question_id)) %>% 
  bind_rows(eval9) %>% 
  write_csv(file = "processed/llm-confidence-correct.csv")
```



